Supporting Information for\\ ``A weakly structured stem for human origins in Africa''

### 2022-08-12 supplement.tex
figure caption

@@

>>>>

\aprcomment{Short paragraph here explaining the discrepancy in the TSI fit
continuous migration model}

@@

\begin{figure}[ht!]
    \centering
    \includegraphics[width=5in]{figures/supp-toy-models}
    \caption{The impact of model specification on coalescence rate and inference.
    We show five simplified demographic models that differ in demographic events, 
    occurring between 200ka and 100ka, that mark the transition between a single 
    ancestral population and two daughter populations. A) A clean split 100ka, 
B) A clean split 200ka, C) population growth at 200ka followed by split 100ka, 
D) split 200ka followed by migration until 100ka, and E) split 200ka followed by 
merger 105ka and a new split 100ka. The left column shows model representation, 
the middle column shows instantaneous coalescence rates for pairs of lineages from the
same daughter population, the right column shows instantaneous coalescence rates for
pairs of lineages coming from distinct populations.  
        \label{fig:toymodels}
    }
    \end{figure}
